Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight Data

### 2011-09-22 extended_catalog/paper/extended_catalog.tex
ading new draft

\newtext{
2FGL\,J0823.0$-$4246 was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
a counts map of this source and overlays and \rosat X-ray contours of
Puppis A.  There are two nearby catalog sources 2FGL\,J0823.4$-$4305
and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
do not appear as separate point-like components.  We concluded that
these nearby point-like sources
were included in 2FGL to account for residual induced
by not modeling the extension of this source and
removed them from our model of the sky.
After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension of
$0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
of $\tsext=46.3$.  Figure~\ref{snr_seds} shows the spectrum of
this source.

@@

\newtext{
2FGL\,J0851.7$-$4635 was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the SNR Vela Jr. This source was recently studied by the LAT
collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
map of the source.  Overlaid on Figure~\ref{Vela_Jr} are \tev
contours of Vela Jr. \citep{vela_jr_hess}.
There are three
point-like catalog sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535,
and 2FGL\,J0855.4$-$4625 which correlate with the 
multiwavelength
emission of
this SNR and were most likely included in 2FGL to account for residual
induced by not modeling the extension Vela Jr.  We removed
from our model of the sky these sources.  In addition, two further away
sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655 were removed from
our model of the sky because they were not significant above 10 \gev.

@@

\newtext{
2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138 were both found to
be extended source candidates in the 10 \gev to 100 \gev energy
range. They are less than $1\degree$ away from each other and needed
to be analyzed simultaneously.  2FGL\,J1615.0$-$5051 is spatially
coincident with the extended \tev source HESS\,J1616$-$508 and
2FGL\,J1615.2$-$5138 is coincident with the extended \tev source
HESS\,J1614$-$518.  Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
of these sources and overlays the \tev contours of HESS\,J1616$-$508 and
HESS\,J1614$-$518 \citep{hess_plane_survey}.  The figure shows that the
2FGL source 2FGL\,J1614.9$-$5212 is very close to 2FGL\,J1615.2$-$5138 and
correlates with the same extended \tev source
as 2FGL\,J1615.2$-$5138.  Therefore, We concluded that
this source were included in 2FGL to account for residual induced by
not modeling the extension of
2FGL\,J1615.2$-$5138 and
remove
it from our model of the sky.  There are two further away sources
2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c that were removed from
our model because they were not significant at energies above 10 \gev.

@@

2FGL\,J1632.4$-$4753c was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range but is in a crowded
region of the sky.  It is spatially coincident with the \tev source
HESS\,J1632$-$478.  Figure~\ref{1FGL_J1632.9-4802c}a shows a counts
map of this source and overlays \tev contours of HESS\,J1632$-$478
\citep{hess_plane_survey}.  The figure shows that there are three nearby
point-like 2FGL sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
2FGL\,J1634.4$-$4743c that correlate with the extended \tev source
but that do not separate from 2FGL\,J1632.4$-$4753c at \gev energies.
we concluded that these point-like 
sources were included in 2FGL to account for
residual induced by not modeling the extension of 
2FGL\,J1632.4$-$4753c
and removed them from our model of the sky.
We also removed four
further away sources 2FGL\,J1638.0$-$4703c, 
2FGL\,J1628.1$-$4857c, 2FGL\,J1630.1$-$4615, 2FGL\,J1639.8$-$4921c because they
were not significant above 10 \gev.

@@

\newtext{
2FGL\,J1837.3$-$0700c was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the \tev source HESS\,J1837$-$069.  This source is
in a complicated region.  Figure~\ref{1FGL_J1837.5-0659c}a shows a
smoothed counts map of the region and overlays the \tev contours of
HESS\,J1837$-$069 \citep{hess_plane_survey}.  There are two very nearby
point-like 2FGL sources 2FGL\,J1836.8$-$0623c, and 2FGL\,J1839.3$-$0558c
that clearly represent distinct sources.  On the other hand, there
is another source 2FGL\,J1835.5$-$0649 located between the three
sources that appears to correlate with the \tev morphology of
HESS\,J1837$-$069 and does not separate from the emission 
of 2FGL\,J1837.3$-$0700c.
We concluded that this source was included in 2FGL to account
for residual induced by not modeling the extension of this source
and removed it from our model of the sky.  We also removed
from our model of the sky the further away point-like 2FGL source
2FGL\,J1839.0-0539 because it was not significant with energies above
10 \gev.  Figure~\ref{1FGL_J1837.5-0659c}b shows a counts map of this
region after subtracted these background sources.

With this model, 2FGL\,J1837.3$-$0700c was found to have an
extension of $0\fdg35\pm0\fdg08_\stat\pm0\fdg03_\sys$ with an extension
significance of $\tsext=18.8$. 
While fitting the extension of 2FGL\,J1837.3$-$0700c,
we iteratively relocalized the three nearby
background sources along with the extension of 2FGL\,J1837.3$-$0700c but
their positions did not significantly change.  2FGL\,J1834.7$-$0705c
moved to $(l,b)=(24\fdg77,0\fdg50)$, 2FGL\,J1836.8$-$0623c moved
to $(l,b)=(25\fdg57,0\fdg32)$, and 2FGL\,J1839.3$-$0558c moved to
$(l,b)=(26\fdg08,0\fdg23)$. With this best fit sky model, we tested for
source confusion by fitting the source instead as two point-like sources.
Because \tsinc is less than \tsext, we concluded that this emission
does not originate from two nearby point-like sources.

@@

There is
a nearby source 2FGL\,J2019.1+4040 that correlates with the radio
emission of $\gamma$-Cygni and does not appear to represent a physically
distinct source.  We concluded that it was included in 2FGL to account for
residual induced by not modeling the extension of $\gamma$-Cygni 
and removed it from our model of the sky.  We also removed from
our model of the sky the four further away sources 2FGL\,J2022.8+3843c,
2FGL\,J2020.0+4159, 2FGL\,J2013.8+4115c, and 2FGL\,J2012.4+3955c because
they were not significant when observed at energies above 10 \gev.
Furthermore, we decided to add to our region an additional point-like
source at $(l,b)=(78\fdg85,2\fdg67)$.  Although this source is not very
significant ($\ts=13.5$ in the 10 \gev to 100 \gev energy range), its
location is outside the 
multiwavelength
contours of $\gamma$-Cygni and
modeling it improved the connection of the best fit extension
with the 
multiwavelength
contours of $\gamma$-Cygni. Nevertheless,
the overall spatial and spectral characteristics of the source were not
significantly changed by the presence of this source.

>>>>

\newtext{
2FGL\,J0823.0$-$4246 was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the SNR Puppis A.  Figure~\ref{1FGL_J0823.3-4248} shows
a counts map of this source and overlays and \rosat X-ray contours of
Puppis A.  There are two nearby catalog sources 2FGL\,J0823.4$-$4305
and 2FGL\,J0821.0$-$4254 that are also coincident with the SNR but that
do not appear to represent physically distinct sources.
We concluded that
these nearby point-like sources
were included in 2FGL to account for residual induced
by not modeling the extension of this source and
removed them from our model of the sky.
After removing these sources, 2FGL\,J0823.0$-$4246 was found to have an extension of
$0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ with an extension significance
of $\tsext=46.3$.  Figure~\ref{snr_seds} shows the spectrum of
this source.

@@

\newtext{
2FGL\,J0851.7$-$4635 was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the SNR Vela Jr. This source was recently studied by the LAT
collaboration in \cite{vela_jr_lat}.  Figure~\ref{Vela_Jr} shows a counts
map of the source.  Overlaid on Figure~\ref{Vela_Jr} are \tev
contours of Vela Jr. \citep{vela_jr_hess}.
There are three
point-like catalog sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535,
and 2FGL\,J0855.4$-$4625 which correlate with the 
multiwavelength
emission of
this SNR but do not appear to be physically distinct sources.
They were most likely included in 2FGL to account for residual
induced by not modeling the extension Vela Jr. and were removed
from our model of the sky.  In addition, two further away
sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655 were removed from
our model of the sky because they were not significant above 10 \gev.

@@

\newtext{
2FGL\,J1615.0$-$5051 and 2FGL\,J1615.2$-$5138 were both found to be
extended source candidates in the 10 \gev to 100 \gev energy range. They
are less than $1\degree$ away from each other and needed to be analyzed
simultaneously.  2FGL\,J1615.0$-$5051 is spatially coincident with
the extended \tev source HESS\,J1616$-$508 and 2FGL\,J1615.2$-$5138
is coincident with the extended \tev source HESS\,J1614$-$518.
Figure~\ref{1FGL_J1613.6-5100c} shows a counts map of these sources and
overlays the \tev contours of HESS\,J1616$-$508 and HESS\,J1614$-$518
\citep{hess_plane_survey}.  The figure shows that the 2FGL source
2FGL\,J1614.9$-$5212 is very close to 2FGL\,J1615.2$-$5138 and correlates
with the same extended \tev source as 2FGL\,J1615.2$-$5138.  We concluded
that this source was included in 2FGL to account for residual induced
by not modeling the extension of 2FGL\,J1615.2$-$5138 and removed
it from our model of the sky.  There are two further away sources
2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c that were removed from
our model because they were not significant at energies above 10 \gev.

@@

2FGL\,J1632.4$-$4753c was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range but is in a crowded
region of the sky.  It is spatially coincident with the \tev source
HESS\,J1632$-$478.  Figure~\ref{1FGL_J1632.9-4802c}a shows a counts
map of this source and overlays \tev contours of HESS\,J1632$-$478
\citep{hess_plane_survey}.  The figure shows that there are three nearby
point-like 2FGL sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
2FGL\,J1634.4$-$4743c that correlate with the extended \tev source
but that do appear to be physically distinct sources.
We concluded that they
were included in 2FGL to account for
residual induced by not modeling the extension of 
2FGL\,J1632.4$-$4753c
and removed them from our model of the sky.
We also removed four
farther away sources 2FGL\,J1638.0$-$4703c, 
2FGL\,J1628.1$-$4857c, 2FGL\,J1630.1$-$4615, 2FGL\,J1639.8$-$4921c because they
were not significant above 10 \gev.

@@

\newtext{
2FGL\,J1837.3$-$0700c was found by our search to be an extended source
candidate in the 10 \gev to 100 \gev energy range and is spatially
coincident with the \tev source HESS\,J1837$-$069.  This source is
in a complicated region.  Figure~\ref{1FGL_J1837.5-0659c}a shows a
smoothed counts map of the region and overlays the \tev contours of
HESS\,J1837$-$069 \citep{hess_plane_survey}.  There are two very nearby
point-like 2FGL sources 2FGL\,J1836.8$-$0623c, and 2FGL\,J1839.3$-$0558c
that clearly represent distinct sources.  On the other hand, there is
another source 2FGL\,J1835.5$-$0649 located between the three sources that
appears to correlate with the \tev morphology of HESS\,J1837$-$069 but
does not appear to represent a physically distinct source.  We concluded
that this source was included in 2FGL to account for residual induced by
not modeling the extension of this source and removed it from our model
of the sky.  We also removed from our model of the sky the farther away
point-like 2FGL source 2FGL\,J1839.0-0539 because it was not significant
with energies above 10 \gev.  Figure~\ref{1FGL_J1837.5-0659c}b shows a
counts map of this region after subtracted these background sources.

With this model, 2FGL\,J1837.3$-$0700c was found to have an
extension of $0\fdg35\pm0\fdg08_\stat\pm0\fdg03_\sys$ with an extension
significance of $\tsext=18.8$. 
While fitting the extension of 2FGL\,J1837.3$-$0700c,
we iteratively relocalized the three nearest
background sources along with the extension of 2FGL\,J1837.3$-$0700c but
their positions did not significantly change.  2FGL\,J1834.7$-$0705c
moved to $(l,b)=(24\fdg77,0\fdg50)$, 2FGL\,J1836.8$-$0623c moved
to $(l,b)=(25\fdg57,0\fdg32)$, and 2FGL\,J1839.3$-$0558c moved to
$(l,b)=(26\fdg08,0\fdg23)$. With this best fit sky model, we tested for
source confusion by fitting the source instead as two point-like sources.
Because \tsinc is less than \tsext, we concluded that this emission
does not originate from two nearby point-like sources.

@@

There is
a nearby source 2FGL\,J2019.1+4040 that correlates with the radio
emission of $\gamma$-Cygni and does not appear to represent a physically
distinct source.  We concluded that it was included in 2FGL to account for
residual induced by not modeling the extension of $\gamma$-Cygni 
and removed it from our model of the sky.  We also removed from
our model of the sky the four farther away sources 2FGL\,J2022.8+3843c,
2FGL\,J2020.0+4159, 2FGL\,J2013.8+4115c, and 2FGL\,J2012.4+3955c because
they were not significant when observed at energies above 10 \gev.
Furthermore, we decided to add to our region an additional point-like
source at $(l,b)=(78\fdg85,2\fdg67)$.  Although this source is not very
significant ($\ts=13.5$ in the 10 \gev to 100 \gev energy range), its
location is outside the 
multiwavelength
contours of $\gamma$-Cygni and
modeling it improved the connection of the best fit extension
with the 
multiwavelength
contours of $\gamma$-Cygni. Nevertheless,
the overall spatial and spectral characteristics of the source were not
significantly changed by the presence of this source.
